Demographic Shifts in Toronto's Homeless Population: Evaluating and Reassessing City Solutions

### 2024-09-27 paper/paper.qmd
3rd edition of limitations

Even though our data is the most up-to-date and accurate data available for the homeless population on Opendatatoronto, it may still have a bias toward the estimation of the true homeless population in the city of Toronto. For example, people would not stay in the shelter every day and they would enter and exit the shelter frequently [@toronto_shelter_data]. Accurately measuring the true population demographic is a very difficult topic even in Canada, but the shelter flow data would provide a proper estimate of our research interest [@dionne2023review]. To understand the problems better and develop more strategies, the next steps would be to research sampling methods that could reach out and survey the population that is difficult to contact such as the unsheltered homeless population. More incorporative sampling strategies would provide us better understanding of homeless demographics and develop further sophisticated plans to reduce homelessness.

>>>>

Although our dataset is the most up-to-date and accurate information available on Opendatatoronto, it remains biased in estimating the true homeless population in Toronto. Individuals do not stay in shelters continuously and frequently cycle in and out of the system [@toronto_shelter_data]. Additionally, as noted in the data section, an estimated 18% of the homeless population does not use the shelter system, making our data underrepresentative of this group. Accurately capturing the full demographic of the homeless population is challenging, even in Canada, but the shelter flow data provides a reasonable estimate for our research purposes [@dionne2023review]. To improve understanding and develop more effective strategies, future research should explore sampling methods that reach hard-to-contact groups, such as the unsheltered homeless. More inclusive sampling approaches would offer a clearer picture of homeless demographics and enable more targeted interventions to reduce homelessness.
